---
title: "Nature Bayesian"
author: Peter Fletcher
Date: 11 May 2020
output: pdf_document
---

# REMEMBER all file paths should be altered to match the file paths you are using!

# Libraries and source code
```{r}
library(pscl)
library(dplyr)
library(survival)
library(readstata13)
# set working directory

```

# Functions 
## Parameters 
* n - total No. pts
* s - number of additional successes REQUIRED after interim for overall GO
* s0 - number of interim success'
* f0 - number of interim failures
* a - beta prior parameter
* b - beta prior parameter

## posterior predictive probability
```{r}
post_pred <- function(n, s, s0, f0, a, b){
  prob <- choose(s + (n - s - s0 - f0), s) * beta(s + s0 + a, (n - s - s0 - f0) + f0 + b) / beta(s0 + a, f0 + b)
  return(prob) 
}
```

## posterior predictive probability of trial 'success' 
```{r}
post_pred_suc <- function(n, s, s0, f0, a, b){
  results <- sapply(s:(n - s0 - f0), post_pred, n = n, s0 = s0, f0 = f0, a = a, b = b)
  names(results) <- paste0('s = ', s:(n - s0 - f0))
  prob<- sum(results)
  #results <- round(results, digits = 5)
  return(prob)
}
```



# Load in data 
```{r, rows.print=2000}

data <- read.csv(file = 'H:/NLMT/DataForR.csv')
data
```

# Analysis 
```{r, rows.print=2000 }
for(i in 1:19){
  # Prior Parameters
  a <- 1
  b <- 1  
  
  # produce posteriors and save plots here:
  setwd('H:/NLMT/Postplots')
 
  plotlim = seq(0.001, 1, by = 0.001)
  
  #OR
  
  # posterior probability true rate is > target rate
  # no targets for Arm C as theis is not a primary outcome for those cohorts
  data[i, 'OR_post'] <- round(pbeta(data$targetrate[i], 
                                     a+data$OR_num[i], 
                                     b +(data$OR_denom[i] - data$OR_num[i]), 
                                     ncp = 0, lower.tail = FALSE, log.p = FALSE) , 3 )
  
  data[i, 'OR_PPoS'] <- round(post_pred_suc(s = (data$target[i] - data$OR_num[i]), n = 30,
                                      s0 = data$OR_num[i], 
                                      f0 = (data$OR_denom[i] - data$OR_num[i]),
                                      a = 1 , b = 1) , 3)
  
  data[i, 'OR_q50']  <- round(qbeta(0.500, 
                                    a + data$OR_num[i],
                                    b + (data$OR_denom[i] - data$OR_num[i])), 3)
  data[i, 'OR_q025'] <- round(qbeta(0.025, 
                                    a + data$OR_num[i], 
                                    b + (data$OR_denom[i] - data$OR_num[i])), 3)
  data[i, 'OR_q975'] <- round(qbeta(0.975, 
                                    a + data$OR_num[i], 
                                    b + (data$OR_denom[i] - data$OR_num[i])), 3)
  

  denspost <- dbeta(plotlim, shape1 = a + data$OR_num[i], shape2 = b + (data$OR_denom[i] - data$OR_num[i]))

  pdf( paste0('postOR_', data[i, 'CohortName'], '.pdf'),   width=16, height=9 )
  plot(plotlim, denspost, xlab = paste0('postOR_', data[i, 'CohortName']) , main='', ylab = '' , type = 'l' ,  cex.lab=2, cex.axis=2)
  abline(v = qbeta(0.5, shape1 = a + data$OR_num[i], shape2 = b + (data$OR_denom[i] - data$OR_num[i])), col = 4, lty = 2)
 dev.off()
  
  #DCB
 
  
  # posterior probability true rate is > target rate
  # no targets for Arm C as theis is not a primary outcome for those cohorts
  data[i, 'DCB_post'] <- round(pbeta(data$targetrate[i], 
                                     a+data$DCB_num[i], 
                                     b +(data$DCB_denom[i] - data$DCB_num[i]), 
                                     ncp = 0, lower.tail = FALSE, log.p = FALSE) , 3 )
  

  data[i, 'DCB_PPoS'] <- round(post_pred_suc(s = (data$target[i] - data$DCB_num[i]), n = 30,
                                       s0 = data$DCB_num[i], 
                                       f0 = (data$DCB_denom[i] - data$DCB_num[i]),
                                       a = 1 , b = 1), 3)
  data[i, 'DCB_q50']  <- round(qbeta(0.500, 
                                    a + data$DCB_num[i],
                                    b + (data$DCB_denom[i] - data$DCB_num[i])), 3)
  data[i, 'DCB_q025'] <- round(qbeta(0.025, 
                                    a + data$DCB_num[i], 
                                    b + (data$DCB_denom[i] - data$DCB_num[i])), 3)
  data[i, 'DCB_q975'] <- round(qbeta(0.975, 
                                    a + data$DCB_num[i], 
                                    b + (data$DCB_denom[i] - data$DCB_num[i])), 3)
  
  
  denspost <- dbeta(plotlim, shape1 = a + data$DCB_num[i], shape2 = b + (data$DCB_denom[i] - data$DCB_num[i]))

  pdf(paste0('postDCB_', data[i, 'CohortName'], '.pdf'),  width=16, height=9 )
  plot(plotlim, denspost, xlab = paste0('postDCB_', data[i, 'CohortName']) , main='', ylab = '' , type = 'l' ,  cex.lab=2, cex.axis=2)
  abline(v = qbeta(0.5, shape1 = a + data$DCB_num[i], shape2 = b + (data$DCB_denom[i] - data$DCB_num[i])), col = 4, lty = 2)
  dev.off()
 
}
data
```


# PPoS code (for arm C)
```{r}

# function TTEPPoS generates PPoS for time to event outcomes

TTEPPoS <- function(n, Y0, T0, r, a, b, crit_val, nsims, pthresh , xfu) {
  
  results <- rep(NA, nsims)
  
  #time_fu <- rep(NA, n)
  #for(i in 1:n) {
  #  time_fu[i] <- (1/r)*(n - i) + xfu
  #}
  
  for(i in 1:nsims){
    
    # we have Y0 events so need n - Y0 events so sample n - Y0 event times
    
    sim_events <- n - Y0
    
    #this is the total time including the time to date
    #T1 <- T0
    
    #sample a mean from the interim posterior distribution
    # keep as mean to be used as rate parameter in the exp distribution
    int_post_mean_time <- rigamma(1, Y0, T0)
    
    
    for(j in 1:sim_events ){
      T1[j] <- rexp(1 , rate = 1/int_post_mean_time)
    }
    

    Ysum <- n # we are assuming here events for all n
    Tsum <- sum(T1) 
    Tsum <- Tsum + T0 # total survival time to date plus simulated
    
    prob <- pigamma(crit_val, a + Ysum, b + log(2)*Tsum) 
    
    
    results[i] <- ifelse(prob < pthresh, 1, 0)
    
  }
  
  return(sum(results)/nsims )
  
} 

```


# calculate TTE PPoS
```{r, rows.print=2000 }
for(i in 1:19){
  
  # this section calculates Posteriors and Predictive Probability of Success for PFS and saves posterior plots here:
  setwd('H:/NLMT/Postplots')
 
# generically true in the standard outcomes
r=1
a=0.001
b=0.001
crit_val=3
nsims=100000   
pthresh=0.5
xfu=0
n = 30
plotlim = seq(0.001, 12, by = 0.1)

# bespoke code for D2 D3 and G1 as their posteriors are off the 12 months scale
#D2
 if (data[i, 'CohortName'] == 'D2') {
  plotlim = seq(0.001, 60, by = 0.1)
}

#D3
 if (data[i, 'CohortName'] == 'D3') {
  plotlim = seq(0.001, 60, by = 0.1)
 }

#G1
 if (data[i, 'CohortName'] == 'G1') {
  plotlim = seq(0.001, 60, by = 0.1)
}
 

# values change per cohort
Y0 = data$PFS_events[i]
T0 = data$PFS_time[i]
T1 <- rep(NA, n-Y0)
results <- rep(NA, nsims)

# checking that there are any events
 if  (Y0>0) {

 data[i, 'PFS_PPoS'] <- round(TTEPPoS(n, Y0, T0, r, a, b, crit_val, nsims, pthresh , xfu) , 3 )
 
 # posteriors and CrI 
 

  # median and percentiles of posterior
  data[i, 'PFS_q50']  <- round(qigamma(.5, a + Y0, log(2)*T0 + b) , 3)
  data[i, 'PFS_q025'] <- round(qigamma(.025, a + Y0, log(2)*T0 + b), 3)
  data[i, 'PFS_q975'] <- round(qigamma(.975, a + Y0, log(2)*T0 + b), 3)

  data[i, 'PFS_q010'] <- round(qigamma(.1, a + Y0, log(2)*T0 + b), 3)
  data[i, 'PFS_q900'] <- round(qigamma(.9, a + Y0, log(2)*T0 + b), 3)

  # Prob true value greater than critical value only really relevant for C
  data[i, 'PFS_post']  <- round(pigamma(crit_val, a + Y0, log(2)*T0 + b) , 3)
  
  denspost <- densigamma(plotlim, alpha = a + Y0, beta = log(2)*T0 + b)

  pdf(paste0('postPFS_', data[i, 'CohortName'], '.pdf'),  width=16, height=9 )
  plot(plotlim, denspost, xlab = paste0('postPFS_', data[i, 'CohortName']) , main='', ylab = '' , type = 'l' ,  cex.lab=2, cex.axis=2)
  abline(v = data[i, 'PFS_q50'] , col = 4, lty = 2)
  dev.off()
  
 }


}
data
```








##  Write data 
```{r}


write.csv(data, file = "H:/NLMT/ResultsFromR.csv")
```







```{r}

# some extra subgroup analysis of smoking and histology

data <- read.csv(file = 'H:/NLMT/SmokeSquamusForR.csv')
data
```


# Analysis 
```{r, rows.print=2000 }
for(i in 1:6){
  # Prior Parameters
  a <- 1
  b <- 1  
  
  setwd('H:/NLMT/')
 
 # plotlim = seq(0.001, 1, by = 0.001)
  
  #OR
 
  data[i, 'OR_q50']  <- round(qbeta(0.500, 
                                    a + data$OR_num[i],
                                    b + (data$OR_denom[i] - data$OR_num[i])), 3)
  data[i, 'OR_q025'] <- round(qbeta(0.025, 
                                    a + data$OR_num[i], 
                                    b + (data$OR_denom[i] - data$OR_num[i])), 3)
  data[i, 'OR_q975'] <- round(qbeta(0.975, 
                                    a + data$OR_num[i], 
                                    b + (data$OR_denom[i] - data$OR_num[i])), 3)
  
}



write.csv(data, file = "H:/NLMT/SmokeSquamousFromR.csv")

```

 































